---
title: "hw3.Rmd"
author: "Seydou Yacouba"
date: "February 18, 2019"
output: html_document
---
```{r}
data(tips, package="reshape2")
summary(tips)
head(tips)
```

```{r}
#1 Number of parties
numParty <- nrow(tips)
numParty
```
```{r}
#2 types of variables in tips
str(tips)

```
```{r}

day <- factor(tips$day, levels = c("Thur", "Fri", "Sat", "Sun"))
day

```
```{r}
female5 <- tips[tips$sex =='Female'& tips$size >=5,]
female5
```
```{r}
library(ggplot2)
ggplot(data = tips, aes(x = total_bill, y = tip)) +
  geom_jitter() +
  scale_x_continuous(breaks = pretty(tips$total_bill, n = 10))
```
From the chart above, one anomaly that I see is where a total bill is about 7 to 8 dollars and pays a tip for more than half of the bill. Its a little bit unusal. 

```{r}
#6
tips$tiprate<- (tips$tip/tips$total_bill)
summary(tips$tiprate)
mean(tips$tipreate)

```

The average rate for tips is 0.1608

```{r}
#7
library(ggplot2)
ggplot(tips, aes(x=factor(time,levels = c("Lunch", "Dinner")) , y=tiprate)) + 
geom_boxplot() + 
scale_x_discrete("time", labels = c("Lunch", "Dinner"))
```
```{r}
#8
ggplot(tips, aes(x = total_bill, y = tip)) +
  geom_jitter() +
  facet_grid( smoker ~ sex) +
  labs(y = "smokers")
```

If we look at the total bill from 30 to 50, We can see the groups of non-smokers have stronger linear relationship with less variability around the linear line.

```{r}
ggplot(tips, aes(x = day, fill = day)) +
  geom_bar() +
  facet_grid(.~sex)

ggplot(tips, aes(x=day, fill=sex))+geom_bar(position="fill")
```

From the chart above we can see that the males pays most of the bills Saturday and Sundays. Firdays and Thursaday are pretty close.



